CALVIS: chest, waist and pelvis circumference from 3D human body meshes as ground truth for deep learning

### 2019-10-29 PaperRMFI2019/samplepaper.tex
fix axilla recognition and mesh signature

\subsection{Human Shape Estimation with Artificial Neural Networks}
A huge amount of research has been conducted in recent years to address the 
problem of 3D/2D human shape estimation using ANNs. A state-of-the-art method 
is \cite{kanazawaHMR18} where they estimate human 
shape and pose. While these ANN's output are human body models parameters 
(i.e., $\beta$s in \cite{Dibra.2016a} and \cite{varol18_bodynet}) our network 
is 
capable to output human dimensions directly.

@@

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
		\includegraphics[width=\linewidth]{axilla_recognition_final.png}
	\end{center}
	\caption{Axilla recognition based on the skeleton joint. We cast a ray from 
		the left shoulder joint $j_{ls}$ in direction to the middle left 
		inferior edge of the bounding box (left). The ray intersects the mesh 
		at point $p_c$ (red) that we consider the axilla center. We plot the 10 
		nearest vertices to $p_c$ (right). Point $p_a$ is the nearest vertex 
		with smallest y coordinate. As it can be observed, the axilla is 
		properly recognized.}
	\label{fig:axilla-recognition}
\end{figure}

\begin{align}
p_c = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
\frac{|v^z_{max} - v^z_{min}|}{2}\bigg).
\end{align}

Here $v^x_{min}, v^y_{min}, v^z_{min}$ are vertex minimum $x$,$y$ and $z$ 
coordinates, respectively; analog is $v^z_{max}$ the maximum vertex $z$ 
coordinate. The ray 
$\iota$ is then determined by points $j_{rs}$ (inside the mesh) and $p_b$ 
(outside the mesh). Therefore, the ray $\iota$ intersects the mesh at one point 
$p_c$ (Figure \ref{fig:axilla-recognition}), which we consider the axilla 
center. Furthermore, we can consider an strategy to increase the method 
robustness against the large variability of the human body. Since this approach 
relies on one point to establish the chest upper bound, we identify the 10 
nearest neighbors in the set of vertices $\mathcal{V}$ to $p_c$ and define 
$p_a$ to be the vertex with the smallest y coordinate of the neighbors.

@@

Note that for cross sections where $\boldsymbol{\pi_j}$ intersects the legs, 
two 
disconnected curves will appear. This is not a problem, because a 
set of disconnected curves is, in our case, a collection of segments with 
non-zero length.

@@

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
		\includegraphics[width=\linewidth]{Figure_1.eps}
	\end{center}
	\caption{Human Body Mesh Signature for male and female meshes. The 
		function resembles a rotated silhouette of the human body and exhibits 
		several \textit{extrema}.}
	\label{fig:hbm_signature}
\end{figure}

>>>>

\subsection{Human Shape Estimation with Artificial Neural Networks}
A huge amount of research has been conducted in recent years to address the 
problem of 3D/2D human shape estimation using CNNs. A state-of-the-art method 
is \cite{kanazawaHMR18} where they estimate human 
shape and pose. While these CNN's output are human body models parameters 
(i.e., $\beta$s in \cite{Dibra.2016a} and \cite{varol18_bodynet}) our network 
is 
capable to output human dimensions directly.

@@

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
		\includegraphics[width=\linewidth]{axilla_recognition_80_NN.png}
	\end{center}
	\caption{Axilla recognition based on the skeleton joint. We cast a ray from 
		the right shoulder joint $j_{rs}$ (red point inside the mesh) in direction to the middle left 
		inferior edge of the bounding box (left). The ray intersects the mesh 
		at point $p_c$ (red) that we consider the axilla center. We plot the 80 
		nearest vertices to $p_c$ (right). Among these vertices point $p_a$ is the vertex 
		with smallest y coordinate. As it can be observed, the axilla is 
		properly recognized.}
	\label{fig:axilla-recognition}
\end{figure}

\begin{align}
p_b = \bigg(v^x_{min}, v^y_{min}, v^z_{min} + 
\frac{|v^z_{max} - v^z_{min}|}{2}\bigg).
\end{align}

Here $v^x_{min}, v^y_{min}, v^z_{min}$ are vertex minimum $x$,$y$ and $z$ 
coordinates, respectively; analog is $v^z_{max}$ the maximum vertex $z$ 
coordinate. The ray 
$\iota$ is then determined by points $j_{rs}$ (inside the mesh) and $p_b$ 
(outside the mesh). Therefore, the ray $\iota$ intersects the mesh at one point 
$p_c$ (Figure \ref{fig:axilla-recognition}), which we consider the axilla 
center. Furthermore, we can consider an strategy to increase the method 
robustness against the large variability of the human body. Since this approach 
relies on one point to establish the chest upper bound, we identify the 80 
nearest neighbors in the set of vertices $\mathcal{V}$ to $p_c$ and define 
$p_a$ to be the vertex with the smallest y coordinate of the neighbors.

@@

@@

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
		\includegraphics[width=\linewidth]{mesh_signature.png}
	\end{center}
	\caption{Human Body Mesh Signature for male and female meshes. The 
		function resembles a rotated silhouette of the human body and exhibits 
		several \textit{extrema}.}
	\label{fig:hbm_signature}
\end{figure}
